Splitting of the homology of the punctured mapping class group

### 2019-07-12 Actiongg.tex
Started the comparison with BoT, reformulated two main theorems

The proof of Theorem \ref{thm:Hbms*as*ggrep} can be easily generalised to surfaces
with more than one boundary component. Let $\Sigma_{g,n}$ be a surface of genus
$g$ with $n\geq 1$ parametrised boundary components and let $\Gamma_{g,n}$ be
the group of connected components of the topological group
$\Diff(\Sigma_{g,n};\partial\Sigma_{g,n})$:
then there is an isomorphism of bigraded $\Z_2$-representations
\begin{equation}
\label{eq:sgn}
\bigoplus_{m\geq 0}H_*\pa{C_m(\Sigma_{g,n})}\simeq \Z_2\left[Q^j\epsilon\,|\, j\geq 0\right]\otimes\Sym_{\bullet}(H_1(\Sigma_{g,n})),
\end{equation}

>>>>

The proof of Theorem \ref{thm:Hbms*as*ggrep} can be easily generalised to surfaces
with more than one boundary curve. Let $\Sigma_{g,n}$ be a surface of genus
$g$ with $n\geq 1$ parametrised boundary curves and let $\Gamma_{g,n}$ be
the group of connected components of the topological group
$\Diff(\Sigma_{g,n};\partial\Sigma_{g,n})$:
then there is an isomorphism of bigraded $\Z_2$-representations
\begin{equation}
\label{eq:sgn}
\bigoplus_{m\geq 0}H_*\pa{C_m(\Sigma_{g,n})}\simeq \Z_2\left[Q^j\epsilon\,|\, j\geq 0\right]\otimes\Sym_{\bullet}(H_1(\Sigma_{g,n})),
\end{equation}

### 2019-07-12 HBraidSurf.tex
Drawn and redrawn figures
Started the comparison with BoT, reformulated two main theorems

In this section and in the next one we will prove the following theorem; to the best of the author's knowledge
it does not appear in the literature.
\begin{thm}
 \label{thm:Hbms*as*ggrep}
 There is an isomorphism of bigraded $\Z_2$-representations of $\gg$
 \[
  \bigoplus_{m\geq 0} H_*\pa{\cms}\simeq \Z_2\left[Q^j\epsilon\,|\, j\geq 0\right]\otimes\Sym_{\bullet}(\H).
 \]
 Here we mean the following:
 \begin{itemize}
  \item[(i)] on the left-hand side the bigrading is given by homological degree $*$ and by the direct summand,
  indexed by $m$,
  on which the homology class is supported, i.e. by the number $m$ of points
  involved in constructing the homology class; we call $*$ the \emph{degree} and $m$ the \emph{weight},
  and write $(*,m)$ for the bigrading;
  \item[(ii)] for $j\geq 0$, $Q^j\epsilon$ is the image in $H_{2^j-1}(C_{2^j}(\S))$ of a generator
  of the group $H_{2^j-1}(C_{2^j}(\D))\simeq \Z_2$ 
  under the natural map induced by the embedding $\D\hookrightarrow\mrS$,
  and $\Z_2\left[Q^j\epsilon\,|\, j\geq 0\right]$ is the polynomial ring on
  infinitely many variables $\epsilon,Q\epsilon,Q^2\epsilon,\dots$;
  \item[(iii)] $\H=H_1(\sg)$ is identified with $H_1(C_1(\S))$ in a natural way, and lives in degree $1$ and weight $1$;
  $\Sym_{\bullet}(\H)$ denotes the symmetric algebra on $\H$;
  \item[(iv)] degrees and weights are extended on the right-hand side by the usual multiplicativity rule;
  \item[(v)] the action of $\gg$ on the right is the tensor product of the trivial action
  on the factor $\Z_2[Q^j\epsilon\,|\, j\geq 0]$, and of the action on
  $\Sym_{\bullet}(\H)$ which is induced by the $\Z_2$-symplectic action on $\H$.
  \end{itemize}
\end{thm}
Note that for any bi-homogeneus element in the right-hand side, the weight is greater or equal than
the degree: indeed factors of the form $Q^j\epsilon$ have weight strictly higher than their degree,
whereas factors belonging to $\H$ or to its symmetric powers have equal weight and degree.

@@

We will mimic the method used by Fuchs \cite{Fuchs:CohomBraidModtwo} to compute the $\Z_2$-cohomology
of $C_m(\D)$.
As already mentioned in section \ref{sec:Preliminaries}, our computation recovers a known result, but it has the advantage of
being quite elementary and of providing a part of
the geometric insight that we will need in the next section.

@@

\begin{figure}\centering
 \includegraphics[scale=0.7]{figures/defTS.pdf}
 \caption{The space $\T(\S)$ for $\S=\Sigma_{3,1}$.}
\label{fig:defTS}
\end{figure}

@@

We note that $\tCh_*(C_p(\Sigma_{0,1})^{\infty})$ is exactly the chain complex described by Fuchs in
\cite{Fuchs:CohomBraidModtwo}: we recall Fuchs' computation of the cohomology of configuration
spaces of the disc, and abbreviate $\D$ for $\mathring{Sigma}_{0,1}$ as in section \ref{sec:Preliminaries}.
\begin{defn}
\label{defn:symchain}
Consider a partition of $p$ into powers of 2
\[
 p=\sum_{j\geq 0}\alpha_j2^j,
\]
and let $\ualpha=(\alpha_j)_{j\geq 0}$ be the sequence of multiplicities. We understand that only finitely
many $\alpha_j$'s are strictly positive.

>>>>

In this section and in the next one we will prove the following theorem; to the best of the author's knowledge
it does not appear in the literature.
\begin{thm}
 \label{thm:Hbms*as*ggrep}
 There is an isomorphism of bigraded $\Z_2$-representations of $\gg$
 \[
  \bigoplus_{m\geq 0} H_*\pa{\cms}\cong \Z_2\left[Q^j\epsilon\,|\, j\geq 0\right]\otimes\Sym_{\bullet}(\H).
 \]
 Here we mean the following:
 \begin{itemize}
  \item[(i)] on the left-hand side the bigrading is given by homological degree $*$ and by the direct summand,
  indexed by $m$,
  on which the homology class is supported, i.e. by the number $m$ of points
  involved in constructing the homology class; we call $*$ the \emph{degree} and $m$ the \emph{weight},
  and write $(*,m)$ for the bigrading;
  \item[(ii)] for $j\geq 0$, $Q^j\epsilon$ is the image in $H_{2^j-1}(C_{2^j}(\S))$ of a generator
  of the group $H_{2^j-1}(C_{2^j}(\D))\simeq \Z_2$ 
  under the natural map induced by the embedding $\D\hookrightarrow\mrS$,
  and $\Z_2\left[Q^j\epsilon\,|\, j\geq 0\right]$ is the polynomial ring on
  infinitely many variables $\epsilon,Q\epsilon,Q^2\epsilon,\dots$;
  \item[(iii)] $\H=H_1(\sg)$ is identified with $H_1(C_1(\S))$ in a natural way, and lives in degree $1$ and weight $1$;
  $\Sym_{\bullet}(\H)$ denotes the symmetric algebra on $\H$;
  \item[(iv)] degrees and weights are extended on the right-hand side by the usual multiplicativity rule;
  \item[(v)] the action of $\gg$ on the right is the tensor product of the trivial action
  on the factor $\Z_2[Q^j\epsilon\,|\, j\geq 0]$, and of the action on
  $\Sym_{\bullet}(\H)$ which is induced by the $\Z_2$-symplectic action on $\H$.
  \end{itemize}
\end{thm}
Note that for any bi-homogeneus element in the right-hand side, the weight is greater or equal than
the degree: indeed factors of the form $Q^j\epsilon$ have weight strictly higher than their degree,
whereas factors belonging to $\H$ or to its symmetric powers have equal weight and degree.

@@

We will mimic the method used by Fuchs \cite{Fuchs:CohomBraidModtwo} to compute the $\Z_2$-cohomology
of $C_m(\D)$.
As already mentioned in Section \ref{sec:Preliminaries}, our computation recovers a known result, but it has the advantage of
being quite elementary and of providing a part of
the geometric insight that we will need in the next section.

@@

\begin{figure}\centering
 \includegraphics[scale=0.7]{figures/defTS.pdf}
 \caption{The space $Q(\S)$ for $\S=\Sigma_{3,1}$. The black pentagons represent the point $\cP_{even}$, whereas the black
 squares represent $\cP_{odd}$.}
\label{fig:defTS}
\end{figure}

@@

We note that $\tCh_*(C_p(\Sigma_{0,1})^{\infty})$ is exactly the chain complex described by Fuchs in
\cite{Fuchs:CohomBraidModtwo}: we recall Fuchs' computation of the cohomology of configuration
spaces of the disc, and abbreviate $\D$ for $\mathring{Sigma}_{0,1}$ as in Section \ref{sec:Preliminaries}.
\begin{defn}
\label{defn:symchain}
Consider a partition of $p$ into powers of 2
\[
 p=\sum_{j\geq 0}\alpha_j2^j,
\]
and let $\ualpha=(\alpha_j)_{j\geq 0}$ be the sequence of multiplicities. We understand that only finitely
many $\alpha_j$'s are strictly positive.

### 2019-07-12 Introduction.tex
Started the comparison with BoT, reformulated two main theorems

\section{Introduction}
Let $\sg$ be a smooth orientable surface of genus $g$ with one boundary component $\partial\sg$, and let $\sgm$ be $\sg$ with
a choice of $m$ distinct points in the interior, called \emph{punctures}.

@@

The main result of this article is that this spectral sequence collapses in its second page.
\begin{thm}
\label{thm:main}
For all $l\geq 0$ there is an isomorphism
\begin{equation}
\label{eq:main}
H_l\pa{\ggm;\Z_2}\cong \bigoplus_{k+q=l} H_k\pa{\gg;H_q\pa{\bms;\Z_2}}.
\end{equation}
\end{thm}
Thus the computation of $H_*\pa{\ggm;\Z_2}$ reduces to the computation of the homology of $\gg$ with
twisted coefficients in the representation $H_*\pa{\bms;\Z_2}$. We will see that this $\ggm$-representation
splits as a direct sum of symmetric powers of $H_1(\sg)$ with the symplectic action
(see Theorem \ref{thm:Hbms*as*ggrep}).
% in section \ref{sec:HBraidSurf}).

@@

>>>>

\section{Introduction}
Let $\sg$ be a smooth orientable surface of genus $g$ with one boundary curve $\partial\sg$, and let $\sgm$ be $\sg$ with
a choice of $m$ distinct points in the interior, called \emph{punctures}.

@@

The main result of this article is that this spectral sequence collapses in its second page.
\begin{thm}
\label{thm:main}
For all $l\geq 0$ there is an isomorphism of vector spaces
\begin{equation}
\label{eq:main}
H_l\pa{\ggm;\Z_2}\cong \bigoplus_{k+q=l} H_k\pa{\gg;H_q\pa{\bms;\Z_2}}.
\end{equation}
\end{thm}
Thus the computation of $H_*\pa{\ggm;\Z_2}$ reduces to the computation of the homology of $\gg$ with
twisted coefficients in the representation $H_*\pa{\bms;\Z_2}$. We will see that this $\gg$-representation
splits as a direct sum of symmetric powers of $H_1(\sg)$ with the symplectic action: this is done in
Theorem \ref{thm:Hbms*as*ggrep}, which together with Theorem \ref{thm:main} is the main result of the article.
% in section \ref{sec:HBraidSurf}).

@@

I would like to thank my PhD advisor Carl-Friedrich B\"odigheimer for his precious suggestions and his continuous encouragement
during the preparation of this work.

### 2019-07-12 Preliminaries.tex
Started the comparison with BoT, reformulated two main theorems

From now on we suppose such an embedding to be fixed and we consider $\D$ as a subspace
of $\mrS$ (see Figure \ref{fig:SS'D}). In Section \ref{sec:HBraidSurf}, Definition \ref{defn:Tsg},
we will introduce a convenient model $\T(\S)$ for the space $\mrS$, and in Section \ref{sec:Actiongg},
Definition \ref{defn:DinTS}
we will specify an embedding $\D\hookrightarrow\mrS$ using the model $\T(\S)$.

@@

\begin{defn}
For all $0\leq p\leq m$ there is a map
\[
 \mu\colon C_p(\D)\times C_{m-p}(\S')\to \cms
\]
which takes the union of configurations (see figure \ref{fig:defmu}):
 \[
  \mu\pa{\set{P_1,\dots,P_p};\set{P'_1,\dots,P'_{m-p}}}=\set{P_1,\dots,P_p,P'_1,\dots,P'_{m-p}}\in\cms.
 \]
\begin{figure}\centering
 \includegraphics[scale=0.7]{figures/defmu.pdf}
 \caption{The product of two configurations in $C_2(\D)$ and $C_4(\S')$.}
\label{fig:defmu}
\end{figure}

@@

In \cite[Chap.III]{CLM} Cohen considers the space $\coprod_{m\geq 0}C_m(\D)$ as an
algebra over the operad of little $2$-cubes, and describes its
$\Z_2$-homology as follows:
\begin{equation}
 \label{eq:Cohen}
H_*\pa{\coprod_{m\geq 0}C_m(\D)}\simeq \Z_2\left[Q^j\epsilon \, |\, j\geq 0\right].
\end{equation}

>>>>

From now on we suppose such an embedding to be fixed and we consider $\D$ as a subspace
of $\mrS$ (see Figure \ref{fig:SS'D}). In Section \ref{sec:HBraidSurf}, Definition \ref{defn:TS},
we will introduce a convenient model $\T(\S)$ for the space $\mrS$, and in Section \ref{sec:Actiongg},
Definition \ref{defn:DinTS}
we will specify an embedding $\D\hookrightarrow\mrS$ using the model $\T(\S)$.

@@

\begin{defn}
\label{defn:muF}
For all $0\leq p\leq m$ there is a map
\[
 \mu\colon C_p(\D)\times C_{m-p}(\S')\to \cms
\]
which takes the union of configurations (see figure \ref{fig:defmu}):
 \[
  \mu\pa{\set{P_1,\dots,P_p};\set{P'_1,\dots,P'_{m-p}}}=\set{P_1,\dots,P_p,P'_1,\dots,P'_{m-p}}\in\cms.
 \]
\begin{figure}\centering
 \includegraphics[scale=0.7]{figures/defmu.pdf}
 \caption{The product of two configurations in $C_2(\D)$ and $C_4(\S')$.}
\label{fig:defmu}
\end{figure}

@@

In \cite[Chap.III]{CLM} Cohen considers the space $\coprod_{m\geq 0}C_m(\D)$ as an
algebra over the operad of little $2$-cubes, and describes its
$\Z_2$-homology as follows:
\begin{equation}
 \label{eq:Cohen}
H_*\pa{\coprod_{m\geq 0}C_m(\D)}\cong \Z_2\left[Q^j\epsilon \, |\, j\geq 0\right].
\end{equation}

### 2019-07-12 Rational.tex
Started the comparison with BoT, reformulated two main theorems

See Figure \ref{fig:rational} to visualize the following discussion.
Let $d$ and $d'$ be disjoint, non-separating simple closed curves such that
the following holds: if we cut $\S$ along $d$ and $d'$ we separate $\S$ into two pieces, one of
which is a subsurface $\S'\simeq\Sigma_{1,2}$ of genus 1, with boundary
components $d$ and $d'$. Here we use that the genus of $\S$ is at least 2.

Suppose now that $c$ is a non-separating simple closed curve in $\S'$,
and let $c',c''$ be two parallel copies of $c$ in $\Sigma_{1,2}$, one on each side of a small tubular
neighborhood of $c$.
Then $d,d',c',c''$ are the boundary of a subsurface $\S''\simeq\Sigma_{0,4}\subset\S'$.
Orient all curves $d,d',c,c',c''$ in such a way that the following equalities hold:
\begin{itemize}
 \item $[d]=[d']\in H_1(\S;\Q)$, as witnessed by the subsurface $\S'$;
 \item $[c]=[c']=[c'']\in H_1(\S;\Q)$;
 \item $[d]-[d']+[c']-[c'']=0\in H_1(\S\setminus c;\Q)$, as witnessed by the subsurface $\S''$.
\end{itemize}

\begin{figure}\centering
 \includegraphics[scale=1.0]{figures/rational.pdf}
 \caption{The curves $d,d',c,c',c'',\gamma,\gamma''$ and the subsurfaces $\S',\S''$.}
\label{fig:rational}
\end{figure}

The four tori $c\times c'$, $c\times c''$, $c\times d$ and $c\times d'$ are contained in $C_2(\S)$
and the equality
\[
 [c\times d]-[c\times d']+[c\times c']-[c\times c'']=0\in H_2(C_2(\S))
\]
holds, as witnessed by the homology $c\times \S''\subset C_2(\S)$.

>>>>

See Figure \ref{fig:rational} to visualize the following discussion.
Let $d$ and $d'$ be disjoint, non-separating simple closed curves such that
the following holds: if we cut $\S$ along $d$ and $d'$ we separate $\S$ into two pieces, one of
which is a subsurface $\tilde{\S}\simeq\Sigma_{1,2}$ of genus 1, with boundary
curves $d$ and $d'$. Here we use that the genus of $\S$ is at least 2.

Suppose now that $c$ is a non-separating simple closed curve in $\tilde{\S}$,
and let $c',c''$ be two parallel copies of $c$ in $\Sigma_{1,2}$, one on each side of a small tubular
neighborhood of $c$.
Then $d,d',c',c''$ are the boundary of a subsurface $\check{\S}\simeq\Sigma_{0,4}\subset\tilde{\S}$.
Orient all curves $d,d',c,c',c''$ in such a way that the following equalities hold:
\begin{itemize}
 \item $[d]=[d']\in H_1(\S;\Q)$, as witnessed by the subsurface $\tilde{\S}$;
 \item $[c]=[c']=[c'']\in H_1(\S;\Q)$;
 \item $[d]-[d']+[c']-[c'']=0\in H_1(\S\setminus c;\Q)$, as witnessed by the subsurface $\check{\S}$.
\end{itemize}

\begin{figure}\centering
 \includegraphics[scale=1.0]{figures/rational.pdf}
 \caption{The curves $d,d',c,c',c'',\gamma,\gamma''$ and the subsurfaces $\tilde{\S},\check{\S}$.}
\label{fig:rational}
\end{figure}

The four tori $c\times c'$, $c\times c''$, $c\times d$ and $c\times d'$ are contained in $C_2(\S)$
and the equality
\[
 [c\times d]-[c\times d']+[c\times c']-[c\times c'']=0\in H_2(C_2(\S))
\]
holds, as witnessed by the homology $c\times \check{\S}\subset C_2(\S)$.

### 2019-07-12 simpleexample.tex
Started the comparison with BoT, reformulated two main theorems

\subsection{Geometric examples of homology classes}
In this subsection we consider the surface $\Sigma_{2,1}$, which we abbreviate with $\S$, and
construct some homology classes in $H_2(C_2(\S))$: our aim is to get a first understanding
of why this homology group is isomorphic to $\Sym_2(\H)=\H^{\otimes 2}/\mathfrak{S}_2$.

>>>>

\subsection{Geometric examples of homology classes}
% \begin{flushright}
%  \textit{An meinen Doktorvater Herr B\"{o}digheimer}
% \end{flushright}

In this subsection we consider the case $g=2$, hence $\S$ denotes the surface $\Sigma_{2,1}$.
We construct some homology classes in $H_2(C_2(\S))$: our aim is to get a first understanding
of why this homology group is isomorphic to $\Sym_2(\H)=\H^{\otimes 2}/\mathfrak{S}_2$.

In the following $c$ and $d$ will always denote two simple closed curves on $\S$, with corresponding homology classes $[c],[d]\in\H$.
\begin{ex}
 \label{ex:one}
Suppose that $c$ and $d$ are as in Figure \ref{fig:exampleone}: $c$ and $d$ are disjoint and non-separating.
We can consider inside $C_2(\S)$
the torus $c\times d$ of configurations in which one of the two points runs along $c$, while the other runs
along $d$. We associate to the fundamental class $\tau_1\in H_2(C_2(\S))$ of this torus the tensor product $[c]\otimes[d]\in\H^{\otimes 2}$.

Since our configurations are unordered and since we work with coefficients in $\Z_2$, the same
class $\tau_1$ can be obtained as a tensor product $[d]\otimes[c]$, i.e. exchanging the order of the two
curves: we can neglect the sign $-1$ that this operation would generate. We represent $\tau_1$ as $[c]\cdot[d]\in\Sym_2(\H)$.
\end{ex}
\begin{figure}[h]\centering
 \includegraphics[scale=1.0]{figures/exampleone.pdf}
 \caption{}
\label{fig:exampleone}
\end{figure}

\begin{ex}
 \label{ex:two}
Suppose that $c$ and $d$ are as in Figure \ref{fig:exampletwo}:
$c$ and $d$ are disjoint, and
 $c$ bounds a subsurface $\check{\S}$ of $\S$ (the shaded region), such that $d$ is not contained in $\check{\S}$.

 Then the homology class $\tau_2=[c]\cdot[d]$ vanishes, because the torus $c\times d$ is the boundary in $C_2(\S)$
 of the 3-manifold $\check{\S}\times d$ containing all configurations in which one point lies on $\check{\S}$ and
 the other on $d$. This is consistent with the representation $\tau_2=[c]\cdot[d]$, because $[c]=0\in \H$.
\end{ex}
\begin{figure}[h]\centering
 \includegraphics[scale=1.0]{figures/exampletwo.pdf}
 \caption{}
\label{fig:exampletwo}
\end{figure}

\begin{ex}
 \label{ex:three}
 Suppose that $c$ and $d$ are as in Figure \ref{fig:examplethree}: $c$ and $d$ are non-separating and 
intersect transversely in one point $P\in\S$. In this case the torus $c\times d$ is a subspace
of $\SP^2(\S)$, but $c\times d$ is not contained in $C_2(\S)$ as in Example \ref{ex:one}.

To solve this problem, we consider a small open neighborhood $P\in \U\subset\S$, and we remove from the torus $c\times d$
all configurations in which both points lie in $\U$: these removed configurations form an open disc inside the torus $c\times d$.

We obtain an embedding $\Sigma_{1,1}\hookrightarrow C_2(\S)$;
the boundary $\partial\Sigma_{1,1}$,
seen as a curve in $C_2(\S)$, is homotopic to a curve $\gamma$ in which one point spins $360^{\circ}$ around the other.
We note that the curve $\gamma\subset C_2(\S)$ is homotopic to a double covering of a curve $\gamma'\subset C_2(\S)$,
in which the two points exchange their positions after spinning $180^{\circ}$ around each other. All curves
$\partial\Sigma_{1,1}$, $\gamma$, $\gamma'$ and the homotopies relating them
are supported on the closure of $C_2(\U)$ in $C_2(\S)$.

We can therefore find a map from a M\"{o}bius band $\M$ to the closure of $C_2(\U)$ in $C_2(\S)$,
such that the images of the curves $\partial\M$ and $\partial\Sigma_{1,1}$ in $C_2(\S)$ coincide.
The union $\Sigma_{1,1}\cup_{\partial}\M$ along the boundary is then a closed
non-orientable surface of genus $3$, i.e. the connected sum of a torus and a projective plane.

The surface $\Sigma_{1,1}\cup_{\partial}\M$ is equipped with a map to $C_2(\S)$, hence its fundamental class with coefficients
in $\Z_2$ yields a homology class $\tau_3\in H_2(C_2(\S))$; thus we have managed to adapt
the construction from Example \ref{ex:one} to the case of two intersecting curves. We represent $\tau_3$
as $[c]\cdot[d]\in\Sym_2(\H)$.
\end{ex}
\begin{figure}[h]\centering
 \includegraphics[scale=1.0]{figures/examplethree.pdf}
 \caption{}
\label{fig:examplethree}
\end{figure}

\begin{ex}
 \label{ex:four}
 Suppose that $c$ and $d$ are as in Figure \ref{fig:examplefour}: $c$ and $d$ are disjoint, and
 $c$ bounds a subsurface $\check{\S}$ of $\S$ (the shaded region), such that $d$ is contained in $\check{\S}$.

 The torus $c\times d$ is contained in $C_2(\S)$, but it is not obvious, at first glance, why its corresponding homology
 class $\tau_4\in H_2(C_2(\S))$ should vanish: the argument used in Example \ref{ex:two} does not work immediately, because the
 3-manifold $\check{\S}\times d$ is only contained in $\SP^2(\S)$ and not in $C_2(\S)$.

 We try to modify this 3-manifold in the same spirit of Example \ref{ex:three}. Let $\U\tilde{\times} d\subset \check{\S}\times d$
 be an open tubular neighborhood of $d\times d$: note that this tubular neighborhood is a trivial bundle over
 $d$ with fiber an open disc $\U$. The notation $\tilde{\times}$ means that abstractly we are dealing with a product $\U\times d$,
 but not geometrically: fibers over different points of $d$ are naturally identified with different discs in $\check{\S}$.

 We consider the 3-manifold $\check{\S}\times d\setminus \U\tilde{\times} d$: its boundary is the disjoint union
 of the torus $c\times d$ and the torus $\partial \pa{\U\tilde{\times} d}$. The latter torus contains configurations of
 two points in $\S$, one of which spins around $d$, whereas the other is a \emph{satellite} of the first and spins
 around it $360^{\circ}$.

 We regard $\partial \U\tilde{\times} d$ as a trivial bundle $\gamma\tilde{\times} d$ over $d$, with fiber the curve $\gamma$
 considered in Example \ref{ex:three}. After a homotopy the latter torus
 becomes a double covering of a torus $\gamma'\tilde{\times} d$: this is a trivial bundle over $d$ with fiber the curve $\gamma'$;
 we can see $\gamma'\tilde{\times} d\subset C_2(\S)$ as a torus of configurations in which the two points
 exchange their positions spinning $180^{\circ}$ around each other, while their barycenter spins around $d$.

 We can fill the second boundary of the $3$-manifold $\check{\S}\times d\setminus \U\tilde{\times} d$
 with the product $\M\times d$: the output is a non-orientable $3$-manifold with boundary $c\times d$, witnessing
 that $\tau_4=0$.

 This is consistent with the representation $\tau_4=[c]\cdot[d]$, because $[c]=0\in \H$.
\end{ex}

\begin{figure}[h]\centering
 \includegraphics[scale=0.8]{figures/examplefour.pdf}
 \caption{}
\label{fig:examplefour}
\end{figure}

\begin{ex}
 \label{ex:five}
 Suppose that $c$ and $d$ are as in Figure \ref{fig:examplefive}:
 $c$ bounds a subsurface $\check{\S}$, and $d$ is cut by $c$ into two arcs, one of which, denoted by $e$, lies
 in $\check{\S}$.

 In this example the complications from Examples \ref{ex:three} and \ref{ex:four} arise at the same time.

 To define the class $\tau_5\in H_2(C_2(\S))$, we start with the torus $c\times d$ and we perform two surgeries
 with two different M\"{o}bius bands to solve the two intersections of $c$ and $d$: the homology
 class that we obtain is represented by a non-orientable surface of genus 4, i.e. the connected
 sum of a torus and 2 projective planes.

 To show that $\tau_5$ vanishes, we start with the 3-manifold with boundary $\check{\S}\times d\subset\SP^2(\S)$ and we perform
 a surgery. We identify with $e$ the arc
 \[
  \check{\S}\times d\cap\pa{\SP^2(\S)\setminus C_2(\S)};
 \]
 this is a properly embedded arc in the 3-manifold with boundary $\check{\S}\times d$, and a tubular neighborhood
 of it, after a suitable homotopy, can be identified with a trivial $\U$-bundle $\U\tilde{\times} e$. We remove
 this solid cylinder from the 3-manifold and glue a trivial $\M$-bundle $\M\tilde{\times} e$, by applying an argument
 similar as the one in Examples \ref{ex:three} and \ref{ex:four}.

 We obtain a 3-manifold with boundary endowed with a map to $C_2(\S)$; the boundary of this 3-manifold
 is precisely the surface used to represent $\tau_5$: therefore $\tau_5=0\in H_2(C_2(\S))$,
 and this is consistent with the representation $\tau_5=[c]\cdot[d]$, because $[c]=0\in \H$.
\end{ex}

\begin{figure}[h]\centering
 \includegraphics[scale=1]{figures/examplefive.pdf}
 \caption{}
\label{fig:examplefive}
\end{figure}

If we consider more than 2 points, the examples become more and more complicated, and proving the theorem with this geometric
approach seems rather difficult.

### 2019-07-12 splitting.tex
Implemented some corrections by cfb, created gitignore file
Started the comparison with BoT, reformulated two main theorems

\documentclass{amsart}
\usepackage{amsmath,amssymb,amsthm,amsfonts,amscd,mathrsfs,mathtools}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[hyphens]{url}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{tikz-cd}

\hyphenation{e-qui-va-riant se-cond ho-mo-lo-gy co-ho-mo-lo-gy}

@@

\theoremstyle{definition}
    \newtheorem{defn}[thm]  {Definition}
    \newtheorem{conj}[thm]{Conjecture}

@@

%\keywords{Topological complexity, aspherical spaces, Lusternik-Schnirelmann category, cohomological dimension, topological robotics, braid groups}
%\subjclass[2010]{55M99, 55P20 (Primary); 55M30, 20J06, 68T40 (Secondary).}

\begin{abstract}
Let $\ggm$ be the mapping class group of an orientable surface $\sgm$ of genus $g$ with one parametrised
boundary component and $m$ permutable punctures, and let $\bms$ be the braid group on $m$ strands
of the surface $\sg$. We prove that $H_*(\ggm;\Z_2)\cong H_*(\gg;H_*(\bms;\Z_2))$. The main ingredient
is the identification of $H_*(\bms;\Z_2)$ as a symplectic representation of $\gg$.
%We compute (?) the right hand side explicitly for $g=1$.
\end{abstract}

@@

\maketitle

@@

\input{Ssequence.tex}
% 
% \input{GenusOne.tex}
% 
\input{Rational.tex}
% 
% \input{Conclusions.tex}

>>>>

\documentclass{amsart}
\usepackage{amsmath,amssymb,amsthm,amsfonts,amscd,mathrsfs,mathtools}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage[hyphens]{url}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{tikz-cd}

\setlength\parindent{0pt}

\hyphenation{e-qui-va-riant se-cond ho-mo-lo-gy co-ho-mo-lo-gy}
% \setlength{\parindent}{6pt}

@@

\theoremstyle{definition}
    \newtheorem{defn}[thm]  {Definition}
    \newtheorem{conj}[thm]{Conjecture}
    \newtheorem{ex}{Example}

@@

\keywords{Mapping class group, braid group, symplectic coefficients.}
\subjclass[2010]{20F36, %Braid groups; Artin groups
55N25, %Homology with local coefficients, equivariant cohomology
55R20, %Spectral sequences and homology of fiber spaces 
55R35, %Classifying spaces of groups and $H$-spaces
55R40, %Homology of classifying spaces, characteristic classes
55R80, %Discriminantal varieties, configuration spaces
55T10, %Serre spectral sequences
}

\begin{abstract}
Let $\Gamma_{g,1}^m$ be the mapping class group of the orientable surface $\Sigma_{g,1}^m$ of genus $g$ with one parametrised
boundary curve and $m$ permutable punctures; when $m=0$ we omit it from the notation.
Let $\beta_{m}(\Sigma_{g,1})$ be the braid group on $m$ strands
of the surface $\Sigma_{g,1}$.

\noindent We prove that $H_*(\Gamma_{g,1}^m;\mathbb{Z}_2)\cong H_*(\Gamma_{g,1};H_*(\beta_{m}(\Sigma_{g,1});\mathbb{Z}_2))$. The main ingredient
is the computation of $H_*(\beta_{m}(\Sigma_{g,1});\mathbb{Z}_2)$ as a symplectic representation of $\Gamma_{g,1}$.
%We compute (?) the right hand side explicitly for $g=1$.

% 
% Let $\Gamma^m_{g,1}$ be the mapping class group of an orientable surface $\Sigma^m_{g,1}$ of genus $g$ with one parametrised
% boundary curve and $m$ permutable punctures, and let $\beta_m(\Sigma_{g,1})$ be the braid group on $m$ strands
% of the surface $\Sigma_{g,1}$ of genus $g$ with one boundary curve.
% 
% We prove that $H_*(\Gamma^m_{g,1};\mathbb{Z}_2)\cong H_*(\Gamma_{g,1};H_*(\beta_m(\Sigma_{g,1});\mathbb{Z}_2))$. The main ingredient
% is the computation of $H_*(\beta_m(\Sigma_{g,1});\mathbb{Z}_2)$ as a symplectic representation of $\Gamma_{g,1}$.
\end{abstract}

@@

\maketitle
THIS VERSION IS NOT ANYMORE UP TO DATE! SEE ARXIVE VERSION

@@

\input{Ssequence.tex}

\input{Comparison.tex}

% \input{Rational.tex}
